\LARGE Tailoring Differentially Private Bayesian Inference to Distance Between Distributions

### 2018-10-11 TPDP2018/poster/main.tex
update poster

\begin{itemize}
  \item[-] The smoothed Hellinger distance based exponential mechanism outperforms asymptotically the baseline 
  approach when the latter uses a sensitivity proportional to dimensionality.
  \item[-] Under the same data set size, $\hexpmech$ can outperform LapMech by increasing the prior.
  % \begin{enumerate}
  %   \item  The accuracy that we are going to explore next, and in a more principled and formal way.

>>>>

\begin{itemize}
  \item[-] The smoothed Hellinger distance based exponential mechanism outperforms asymptotically the baseline 
  approach but not the improved one.
  \item[-] Under the same data set size, $\hexpmech$ can outperform LapMech by increasing the prior.
  % \begin{enumerate}
  %   \item  The accuracy that we are going to explore next, and in a more principled and formal way.
